Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-02-27 introduction.tex
making progress with the introduction

Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}]. These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}}. While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk in high and therefore more complete and accurate assessments of seismic hazard are necessary.

>>>>

Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}]. These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}. While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk is high and therefore more complete and accurate assessments of seismic hazard are necessary.
